Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-23 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add new images 512 x 512

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{graphicx}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
  # - \usepackage{pgf}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

\newcommand{\bias}{\operatorname{Bias}}

@@

The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical}. 
It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. 
In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.

```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

R <- 3000
mu <- 1
L <- 8
B <- 1
sample.size <- c( 121)

alpha1_values <- c(-3, -8, -20, -1000)

@@

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

@@

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Empirical Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@

```
## Estimation of the Shannon Entropy

@@

In Fig. \ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

estimators_to_table <- c("Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap")

filtered_results <- purrr::map_dfr(results_gi0, ~ .x %>% filter(Estimator %in% estimators_to_table), .id = "mu")

@@

#
print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE, 
    digits = 3,  
    label = "table2"  
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
)
```

@@

Fig. \ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness, kurtosis, and Anderson–Darling $p$-values for normality. 
Results with $p$-values $> 0.05$  indicate no evidence against normality. 
Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails, aligning with normal distribution expectations.

@@

```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 500
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

all_summary_stats <- list()
all_TestStatistics <- list()
#all_TestNormality <- list()
#all_plots <- list()

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              CV= numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )  # Nueva columna para  L
  # summary_normality <- data.frame(Sample_Size = numeric(),
  #                               lillie_p_value = numeric(),
  #                               ad_p_value = numeric())
  #normality_test <- list()#

@@

    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
    #                                                          SampleSize = s,
    #                                                          lilliepvalue = lillie_p_value,
    #                                                          adpvalue = ad_p_value))
  }

  all_TestStatistics[[as.character(L)]] <- TestStatistics1
  all_summary_stats[[as.character(L)]] <- summary_stats
  #all_TestNormality[[as.character(L)]] <- summary_normality

#save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

@@

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle")# %>%
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

@@

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

@@

>>>>

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{graphicx}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   #- \usepackage{subcaption}
   - \usepackage{pgf}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

\newcommand{\bias}{\operatorname{Bias}}
\setlength{\tabcolsep}{4pt}

@@

The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical_gamma_and_gi0}. 
It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. 
In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.

```{r Simulated_empirical_gamma_and_gi0, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 3000
mu <- 1
L <- 8
B <- 1
sample.size <- c(121)
alpha1_values <- c(-3, -8, -20, -1000)

TestStatisticsList <- list()

for (alpha_val in alpha1_values) {
  alpha1 <- alpha_val
  TestStatistics1 <- NULL
  TestStatistics2 <- NULL

@@

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
    }

@@

  TestStatisticsList[[as.character(alpha_val)]] <- list(TestStatistics1 = TestStatistics1, TestStatistics2 = TestStatistics2)
}

save(TestStatisticsList, file = "./Data/data_empirical_entropy.RData")

```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

load("./Data/data_empirical_entropy.Rdata")
plots_list <- list()

for (alpha_val in alpha1_values) {
  plot_data <- TestStatisticsList[[as.character(alpha_val)]]

  max_density1 <- max(density(plot_data$TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
  max_density2 <- max(density(plot_data$TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)

  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Empirical Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@

## Estimation of the Shannon Entropy

@@

In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/results_gi0.Rdata")

# Define estimators
estimators_to_table <- c("Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap")

# Filter and reshape data
filtered_results <- purrr::map_dfr(results_gi0, ~ .x %>% filter(Estimator %in% estimators_to_table), .id = "mu")

@@

reshaped_results[] <- lapply(reshaped_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrrr",
    escape = FALSE, 
    digits = 3,  
    label = "table2"
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "c")
    #kable_styling(latex_options = "hold_position", "scale_down")
  )

@@

Fig. \ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality. 
Results with $p$-values $> 0.05$  indicate no evidence against normality. 
Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails. The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases, aligning with normal distribution expectations.

@@

```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 100
mu <- 1
B <- 1
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300)
L_values <- c(2, 5, 8, 18)

all_summary_stats <- list()
all_TestStatistics <- list()

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              CV= numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )

@@

  all_TestStatistics[[as.character(L)]] <- TestStatistics1
  all_summary_stats[[as.character(L)]] <- summary_stats

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

cat("\\setlength{\\tabcolsep}{1.0pt}\n")

@@

# LaTeX notation for negative numbers and integers
combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
  #table.env = 'table*' # to span multiple columns
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

    for (r in 1:R) {

      z <- gamma_sar_sample(L, mu, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      z1 <- gi0_sample(mu, alpha1, L, s)
      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z1, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        #(L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

@@

## Experiments on Real SAR Images

To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band,with  HH polarization, and intensity format. The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.

We evaluate the test accuracy with small data portions. Ensuring resistance to contamination is crucial, especially in small samples with $5\times 5$, $7\times 7$, or $9\times 9$ windows that may contain data from areas with varying textures. Our assessment determines if the test can produce reasonable estimations, even when some data deviates from the assumed model.

Table&nbsp;\ref{tab:table_sar} shows the results for $5 \times 5$ windows, detailing the performance of the proposed test in accurately identifying the origin of the data. The metadata associated with these original SAR images includes a number of looks $L = 5$.

The openly accessible Sentinel-1 data used in this study was downloaded as Level-1 Ground Range Detected (GRD) products from the Copernicus Data Space Ecosystem (\url{https://dataspace.copernicus.eu}). This format, gaining popularity among operational and application users, containing only the co-polarized and cross-polarized backscatter intensities (VV, VH).

```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")
```

```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")
x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')

L <- 5
B <- 10

# Brazil
nRows_Brazil <- 512
nCols_Brazil <- 512

centerRow_Brazil <- floor(nRows_Brazil / 2)
centerCol_Brazil <- floor(nCols_Brazil / 2)

roiSize_Brazil <- 5

# Coordinates of the ROI
roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1

roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1

# Extract the ROI
roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]

mean_data_brasil <- mean(roi_Brazil)
Entropy_brasil <- correa_estimator(roi_Brazil)
entropia_estimada_boot_brasil <- bootstrap_correa_estimator(roi_Brazil, B)
True_entropy_brasil <- (log(mean(roi_Brazil)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_brasil <- bootstrap_correa_estimator_log_mean(roi_Brazil, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Berlin
nCols_Berlin = 512
nRows_Berlin = 512

centerRow_Berlin <- floor(nRows_Berlin / 2)
centerCol_Berlin <- floor(nCols_Berlin / 2)

roiSize_Berlin <- 5

# Calculate ROI coordinates
roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1

roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1

# Extract the ROI
roi_Berlin <- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]

mean_data_Berlin <- mean(roi_Berlin)
Entropy_Berlin <- correa_estimator(roi_Berlin)
entropia_estimada_boot_Berlin <- bootstrap_correa_estimator(roi_Berlin, B)
True_entropy_Berlin <- (log(mean(roi_Berlin)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_Berlin <- bootstrap_correa_estimator_log_mean(roi_Berlin, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Flevoland
nCols_Flevoland = 512
nRows_Flevoland = 512

centerRow_Flevoland <- floor(nRows_Flevoland / 2)
centerCol_Flevoland <- floor(nCols_Flevoland / 2)

roiSize_Flevoland <- 5

# ROI coordinates
roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1

roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1

# Extract the ROI
roi_Flevoland <- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]

mean_data_Flevoland <- mean(roi_Flevoland)
Entropy_Flevoland <- correa_estimator(roi_Flevoland)
entropia_estimada_boot_Flevoland <- bootstrap_correa_estimator(roi_Berlin, B)
True_entropy_Flevoland <- (log(mean(roi_Flevoland)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_Flevoland <- bootstrap_correa_estimator_log_mean(roi_Flevoland, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Ottawa
nCols_Ottawa = 512
nRows_Ottawa = 512

centerRow_Ottawa <- floor(nRows_Ottawa / 2)
centerCol_Ottawa <- floor(nCols_Ottawa / 2)

roiSize_Ottawa <- 5

# ROI coordinates in the upper part
roiUpperStartRow <- 1
roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1

roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1

# Extract the ROI in the upper part
roi_Ottawa <- x_Ottawa[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]

mean_data_Ottawa <- mean(roi_Ottawa)
Entropy_Ottawa <- correa_estimator(roi_Ottawa)
entropia_estimada_boot_Ottawa <- bootstrap_correa_estimator(roi_Ottawa, B)
True_entropy_Ottawa <- (log(mean(roi_Ottawa)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_Ottawa <- bootstrap_correa_estimator_log_mean(roi_Ottawa, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Save results
resultados_df <- data.frame(
  Ciudad = c("Amazonas", "Berlin", "Flevoland", "Ottawa"),
  Media = c(mean_data_brasil, mean_data_Berlin, mean_data_Flevoland, mean_data_Ottawa),
  Entropia_Estimada = c(Entropy_brasil, Entropy_Berlin, Entropy_Flevoland, Entropy_Ottawa),
  Entropia_Estimada_Boot = c(entropia_estimada_boot_brasil, entropia_estimada_boot_Berlin, entropia_estimada_boot_Flevoland, entropia_estimada_boot_Ottawa),
  Entropia_Verdadera = c(True_entropy_brasil, True_entropy_Berlin, True_entropy_Flevoland, True_entropy_Ottawa),
  Diferencia_Test_Entropia = c(Test_difference_brasil, Test_difference_Berlin, Test_difference_Flevoland, Test_difference_Ottawa)
)

colnames(resultados_df) <- c("Area", "Mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(\\bm Z)$")

save(resultados_df, file = "./Data/resultados_df.Rdata")

```{r Table_SAR_simulations, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat("\\setlength{\\tabcolsep}{4pt}\n")
 load("./Data/resultados_df.Rdata")

resultados_df[] <- lapply(resultados_df, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

print(
  kbl(
    resultados_df,
    caption = "Results of applying the statistical test to SAR images.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrr",
    escape = FALSE,
    digits = 4,
    label = "table_sar",
    linesep = "",
  ) %>%
    #kable_styling(latex_options = "hold_position") %>%
    row_spec(0,  align = "c")# %>%

)
